\ttitle

### 2015-06-15 Chapters/BodyComp.tex
Some minor changes before starting work today
Additions to results section of CPET Survival
- Add description of results of Cox regression to CPET Survival
- Shorten cpet_survival_cox_regression table by condensing rows into one per parameter
- Save long form of above table in separate file - not currently in use
- New table - cpet_survival_6months - needs fleshing out
- Add todo to BodyComp chapter - ?relationship with systemic inflammation
- Changes to main are simply variations in included files

% Chapter 04

\chapter{An investigation into the relationship between cardiopulmonary exercise testing and body composition in patients undergoing major pancreatic surgery.}
\label{ch_bodycomp}

@@

\clearpage
%----------------------------------------------------------------------------------------
$\dot{V}_{O_2}$
\section{Introduction}
Major abdominal surgery especially for pancreatic disease is associated with significant morbidity and mortality. Patient selection is as important as identifying surgical treatable pathology in ensuring optimal outcomes. \parencite{balthazar_acute_2002}

@@

Current convention is to report $\dot{V}_{O_2}$ measured at cardiopulmonary exercise testing according the following formula: 
\[Corrected\ VO_2 (mls.kg^{-1}.min^{-1}) = \frac{Absolute\ VO_2\ (litres.min^{-1}) * 1000}{Total\ body\ weight\ (kg)}\]

>>>>

% Chapter 04
\chapter{An investigation into the relationship between cardiopulmonary exercise testing and body composition in patients undergoing major pancreatic surgery.}
\label{ch_bodycomp}

@@

\clearpage
%----------------------------------------------------------------------------------------
\todo{Consider including relationship with systemic inflammation}

zotero - richards-relationships-2012

\section{Introduction}
Major abdominal surgery especially for pancreatic disease is associated with significant morbidity and mortality. Patient selection is as important as identifying surgical treatable pathology in ensuring optimal outcomes. \parencite{balthazar_acute_2002}

@@

Current convention is to report $\dot{V}_{O_2}$ measured at cardiopulmonary exercise testing according the following formula: 
\[Corrected\ \dot{V}_{O_2} (mls.kg^{-1}.min^{-1}) = \frac{Absolute\ \dot{V}_{O_2}\ (litres.min^{-1}) * 1000}{Total\ body\ weight\ (kg)}\]

### 2015-06-15 Chapters/CPET_Survival.tex
CPET Survival Cox Univariate regression
- Complete CPET vs Survival Univariate table
- Create new SPSS dataset for this chapter -ds_at_pdac
- Remove redundant variables in this dataset
- Changes to main.tex are simply commenting out other chapters from output
Add cpet_survival_cox_regression table to Tables
- Include table in chapter CPET Survival
Additions to results section of CPET Survival
- Add description of results of Cox regression to CPET Survival
- Shorten cpet_survival_cox_regression table by condensing rows into one per parameter
- Save long form of above table in separate file - no

% Chapter 05 - CPET, complications and survival

@@

>>>>

% Chapter 05 - CPET, comorbidity and survival

@@

\input{Tables/cpet_survival_cox_regression}

Fifty patients (31 male) with pancreatic ductal adenocarcinoma underwent pancreaticoduodenectomy (n=48) or sub-total pancreatectomy (n=2) and had cardiopulmonary exercise test as part of their preoperative assessment. The median age of the patients was xx (range ). Three patients died within 30 days of the operation as a result of postoperative complications and were excluded from the survival analysis.

%UNIVARIATE Cox-regression analysis
The clinico-pathological characteristics of the patients studied (n=47) are shown in \ref{table:cpet_survival_cox} on p\pageref{table:cpet_survival_cox}. POSSUM Physiology score $>$14 (HR 2.38, 95\% CI 1.19 - 4.75, p = 0.014) and preoperative serum C-reactive protein $>$ 10 mg/dl (HR 2.14, 95\% CI 1.04 - 4.41, p = 0.04) were associated with survival on univariate Cox-regression analysis. Cardiopulmonary exercise test parameters including $\dot{V}_{O_2}$AT, $\dot{V}_{O_2}$Peak and $\dot{V}_E/\dot{V}_{CO_2}$ were not associated with survival on univariate analysis.
%MULTIVARIATE Cox-regression analysis
On multi-variate backward conditional regression analysis using POSSUM Physiology Score and serum C-reactive protein as independent variables, only POSSUM Physiology Score $>$14  was found to be an independent predictor of survival (HR 2.38, 95\% CI 1.19 - 4.75, p = 0.014).

%Create a table looking at means of cardiopulmonary exercise test parameters in survivors vs. non-survivors at 6 months, 1 year and 2 years. This should give three tables. as below.

\input{Tables/cpet_survival_6months}
